Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2019-03-28 SupportingInformation.Rmd

```{r overwritting_plots_asym_cop,echo=F,results="hide"}
pdf("./Results/asym_sens_results/a_0.2_b_0.1_r_0.8_asym_sens.pdf",height=3,width=6)
op<-par(mfrow=c(1,2),mar=c(3.5,4,1,1),mgp=c(2.2,0.5,0))
pop<-ans_b_0.1$pop
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,
     cex.axis=1,col=rgb(0,0,0,0.5),pch=20,cex=0.6)
text(0.1,0.95,"A",cex=2)
pop<-ans_b_0.1$pop_d
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,
     cex.axis=1,pch=20,col=rgb(0,0,0,0.5),cex=0.6)
text(0.1,0.95,"B",cex=2)
par(op)
dev.off()

pdf("./Results/asym_sens_results/a_0.2_b_-0.1_r_0.8_asym_sens.pdf",height=3,width=6)
op<-par(mfrow=c(1,2),mar=c(3.5,4,1,1),mgp=c(2.2,0.5,0))
pop<-ans_b_neg0.1$pop
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,
     cex.axis=1,pch=20,col=rgb(0,0,0,0.5),cex=0.6)
text(0.1,0.95,"A",cex=2)
pop<-ans_b_neg0.1$pop_d
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,
     cex.axis=1,col=rgb(0,0,0,0.5),pch=20,cex=0.6)
text(0.1,0.95,"B",cex=2)
par(op)
dev.off()

pdf("./Results/asym_sens_results/a_0.2_b_0.5_r_0.8_asym_sens.pdf",height=3,width=6)
op<-par(mfrow=c(1,2),mar=c(3.5,4,1,1),mgp=c(2.2,0.5,0))
pop<-ans_b_0.5$pop
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,
     cex.axis=1,col=rgb(0,0,0,0.5),pch=20,cex=0.6)
text(0.1,0.95,"A",cex=2)
pop<-ans_b_0.5$pop_d
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,
     cex.axis=1,col=rgb(0,0,0,0.5),pch=20,cex=0.6)
text(0.1,0.95,"B",cex=2)
par(op)
dev.off()

pdf("./Results/asym_sens_results/a_0.2_b_-0.5_r_0.8_asym_sens.pdf",height=3,width=6)
op<-par(mfrow=c(1,2),mar=c(3.5,4,1,1),mgp=c(2.2,0.5,0))
pop<-ans_b_neg0.5$pop
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,
     cex.axis=1,col=rgb(0,0,0,0.5),pch=20,cex=0.6)
text(0.1,0.95,"A",cex=2)
pop<-ans_b_neg0.5$pop_d
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,
     cex.axis=1,col=rgb(0,0,0,0.5),pch=20,cex=0.6)
text(0.1,0.95,"B",cex=2)
par(op)
dev.off()
```

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/asym_sens_results/a_0.2_b_0.5_r_0.8_asym_sens.pdf}
\caption{Analogous to Fig. \ref{MT-fig_ms_asym_b_0.1}, but using $b=0.9$.\label{fig_ms_asym_b_0.5}}
\end{center}
\end{figure}

\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/asym_sens_results/a_0.2_b_-0.5_r_0.8_asym_sens.pdf}
\caption{Analogous to Fig. \ref{MT-fig_ms_asym_b_0.1}, but using $b=-0.9$.\label{fig_ms_asym_b_-0.5}}
\end{center}
\end{figure}

>>>>

```{r overwritting_plots_asym_cop,echo=F,results="hide"}
pdf("./Results/asym_sens_results/a_0.2_b_0.1_r_0.8_asym_sens.pdf",height=3,width=6)
op<-par(mfrow=c(1,2),mar=c(3.5,4,1,1),mgp=c(2.2,0.5,0))
pop<-ans_b_0.1$pop
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,
     cex.axis=1,col=rgb(0,0,0,0.2),pch=20,cex=0.6)
text(0.1,0.95,"A",cex=2)
pop<-ans_b_0.1$pop_d
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,
     cex.axis=1,pch=20,col=rgb(0,0,0,0.2),cex=0.6)
text(0.1,0.95,"B",cex=2)
par(op)
dev.off()

pdf("./Results/asym_sens_results/a_0.2_b_-0.1_r_0.8_asym_sens.pdf",height=3,width=6)
op<-par(mfrow=c(1,2),mar=c(3.5,4,1,1),mgp=c(2.2,0.5,0))
pop<-ans_b_neg0.1$pop
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,
     cex.axis=1,pch=20,col=rgb(0,0,0,0.2),cex=0.6)
text(0.1,0.95,"A",cex=2)
pop<-ans_b_neg0.1$pop_d
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,
     cex.axis=1,col=rgb(0,0,0,0.2),pch=20,cex=0.6)
text(0.1,0.95,"B",cex=2)
par(op)
dev.off()

pdf("./Results/asym_sens_results/a_0.2_b_0.5_r_0.8_asym_sens.pdf",height=3,width=6)
op<-par(mfrow=c(1,2),mar=c(3.5,4,1,1),mgp=c(2.2,0.5,0))
pop<-ans_b_0.5$pop
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,
     cex.axis=1,col=rgb(0,0,0,0.2),pch=20,cex=0.6)
text(0.1,0.95,"A",cex=2)
pop<-ans_b_0.5$pop_d
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,
     cex.axis=1,col=rgb(0,0,0,0.2),pch=20,cex=0.6)
text(0.1,0.95,"B",cex=2)
par(op)
dev.off()

pdf("./Results/asym_sens_results/a_0.2_b_-0.5_r_0.8_asym_sens.pdf",height=3,width=6)
op<-par(mfrow=c(1,2),mar=c(3.5,4,1,1),mgp=c(2.2,0.5,0))
pop<-ans_b_neg0.5$pop
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,
     cex.axis=1,col=rgb(0,0,0,0.2),pch=20,cex=0.6)
text(0.1,0.95,"A",cex=2)
pop<-ans_b_neg0.5$pop_d
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,
     cex.axis=1,col=rgb(0,0,0,0.2),pch=20,cex=0.6)
text(0.1,0.95,"B",cex=2)
par(op)
dev.off()
```

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/asym_sens_results/a_0.2_b_0.5_r_0.8_asym_sens.pdf}
\caption{Analogous to Fig. \ref{MT-fig_ms_asym_b_0.1}, but using $b=0.5$.\label{fig_ms_asym_b_0.5}}
\end{center}
\end{figure}

\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/asym_sens_results/a_0.2_b_-0.5_r_0.8_asym_sens.pdf}
\caption{Analogous to Fig. \ref{MT-fig_ms_asym_b_0.1}, but using $b=-0.5$.\label{fig_ms_asym_b_-0.5}}
\end{center}
\end{figure}
